Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-22 Background.tex
Wordings

\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \ac{FFH}. This recasts rationality as bound to the context of the behaviour - a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical. On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment, which implies that heuristics are task specific.

@@

While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models. The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986} . \citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics. The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
This last, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.

\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed. While an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e. in situations of intertemporal choice. Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this. More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential, although neither model is complete - both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains. \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.

>>>>

\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \acp{FFH}. This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical. On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment \citep{Todd2003}, which implies that heuristics are task specific. They provide a number of heuristics for varying decision problems, e.g. recognition \citep{Goldstein2002}, cue ordering \citep{Gigerenzer1999,Todd2004}, and binary decisions \citep{Brandstatter2006}.

@@

While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models. The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986}. \citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics. The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
This last, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.

\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed. While an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e. in situations of intertemporal choice. Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this. More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential. However neither model is complete, in that both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains. \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.

### 2014-07-22 Introduction.tex
Wordings

This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \ac{RCT} are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.

>>>>

This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.

### 2014-07-22 Methods.tex
Wordings

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.

>>>>

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
